European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-24 manuscript/manuscript.qmd
Add declarations (#68)

::: {.data-availability}
**Data Availability Statement**  The replication files for this paper are available at [https://github.com/IMFPaper/IMF](https://github.com/IMFPaper/IMF).
:::

::: {.funding}
**Funding Statement**  This research is not funded.
:::

::: {.competing-interests}
**Competing Interests**  The authors declare none.
:::

>>>>

::: {.data-availability}
**Data Availability Statement**

The replication files for this paper are available at [https://github.com/IMFPaper/IMF](https://github.com/IMFPaper/IMF).
:::

::: {.funding}
**Funding Statement**

This research is not funded.
:::

::: {.competing-interests}
**Competing Interests**

The authors declare none.
:::
